### 2016-07-14 2016_Proceedings_ISMIR/tutorials.tex
re-added author index title page, updated preface and tutorials

% Tutorial 2
\includetut{Music Information Retrieval: Overview, Recent
  Developments and Future Challenges}{Emilia G\'omez, Markus Schedl,
  Xavier Serra, Xiao Hu}{3}

% Tutorial 3
\includetut{Why is studio production interesting?}{Emmanuel
Deruty, Fran\c{c}ois Pachet}{4-5}

% Tutorial 4
\includetut{Introduction to EEG Decoding for Music Information Retrieval
Research}{Sebastian Stober, Blair Kaneshiro}{6}

% Tutorial 5
\includetut{Natural Language Processing for MIR}{Sergio Oramas,
  Luis Espinosa-Anke, Shuo Zhang, Horacio Saggion}{7}

% Tutorial 6
\includetut{Why Hip-Hop is interesting}{Jan Van Balen, Ethan
  Hein, Dan Brown}{8-9}

>>>>

% Tutorial 2
\includetut{Music Information Retrieval: Overview, Recent
  Developments and Future Challenges}{Emilia G\'omez, Markus Schedl,
  Xavier Serra, Xiao Hu}{3-4}

% Tutorial 3
\includetut{Why is studio production interesting?}{Emmanuel
Deruty, Fran\c{c}ois Pachet}{5-6}

% Tutorial 4
\includetut{Introduction to EEG Decoding for Music Information Retrieval
Research}{Sebastian Stober, Blair Kaneshiro}{7-8}

% Tutorial 5
\includetut{Natural Language Processing for MIR}{Sergio Oramas,
  Luis Espinosa-Anke, Shuo Zhang, Horacio Saggion}{9-10}

% Tutorial 6
\includetut{Why Hip-Hop is interesting}{Jan Van Balen, Ethan
  Hein, Dan Brown}{11-12}
